Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-04-21 paper/ms.tex
Add citation to Fragkoudi

>>>>

\citet{2021AA...650L..16F} explored the evolution of bars in the Auriga
cosmological zoom simulations \citep{2017MNRAS.467..179G}. They find \Rot{}
values consistent with observations. Furthermore, their pattern speed evolution
shows some apparent periods of stability (see their Fig.~B1). One galaxy, Au27,
appears to even transition from the stable pattern speed regime to the slowing
down regime at a lookback time of $\sim1.8\,\textrm{Gyr}$.
